### 2019-04-02 manuscript.tex
Update manuscript.tex

The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.  The progress is hindered due to the complicated history of the very practice \cite{Cami16}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.

@@

\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, more} and other norm studies of why mother cut daughters etc}

@@

Our findings showed that women’s decision on cutting their daughters was clearly associated with their own FGC status and beliefs in FGC benefits at a population (?) level and FGC prevalent at a community level; the results also applied to their views of FGC continuity .  However, the women’s beliefs of FGC benefits in cutting women at a community level did not play as a clear factor in all the three FGC preferences.  Our findings implies that the practice of FGC is a social norm in terms of how a community as a whole carried out the practice.

Regarding the daughter model,

--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
\cfcmt{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.

--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}

@@

-- Second interpretation --
--- socio demographic interpretation at both levels (link this to modernization?)
\cite{Hayf05, PashPonn16} (more)
% education:  \cite{IliyAbub12, KarmKand11}
% religion:  \cite{KarmKand11}

\cfcmt{feminism or women’s rights perspective:  which women?  Who are the women?  Women from the West or women from inside the fgc communities?}

% “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})

--- by nations
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

@@

==========

% FGC laws in those nations
% collective action problem referring to community level of impact
Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}. It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).

% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.

@@

% If convention theory is more than just about securing marriage market (e.g., peer convention), then it is a theory about norms in general, isn't it?  That is, types of norms explain better than just marriage market.

@@

% Others:

@@

% \cite{BergDeni13}: application/public policy ``A realist synthesis of controlled studies to determine the effectiveness of interventions to prevent genital cutting of girls.``

@@

A synthesis of context studies of Africa showed that the main factors that supported FGC were tradition, religion, and reduction of women's sexual desire, and the main factors hindered FGM/C were medical complications and prevention of sexual satisfaction. \cite{BergDeni12a}.  For example, in Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.  In Kenya, woman's decision on whether to cut their daughters' genitals were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.

@@

% `` the effectiveness of interventions was hampered by a general lack of information. However, through the realist synthesis we identified that all of the interventions were based on a theory that dissemination of information improves cognitions about FGM/C, but the interventions' success was contingent upon a range of contextual factors. `` \cite{BergDeni12a}

@@

It is inevitable to compare male circumcision to female genital cutting and question how male circumcision gain its cultural recognition but not FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} may be an alternative without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative thought.)

To study types of FGC for the future to understand correlation/assocaition between types of fgc and fgc beneifts.

--- questions worth addressing
1. Is there a tipping point?  Can our findings disclose some ideas on fgc intervention in terms of behavioural change in order to reach a tipping point?

_ Following up project:
 Threshold on FGC:  based on our finding, mother’s FGC status and community FGC prevalence is a good predictor of daughter’s future FGC status.  We can use newer DHS of multiple nations to predict the future of FGC practice.  We can use data without fgc benefit module, and that will give us more data than the current 4 nations.

\subsection{Funding}\label{Funding}

>>>>

The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.  The progress is hindered due to the complicated history of the very practice \cite{Cami16}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.

@@

\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, ShelWand11, more} and other norm studies of why mother cut daughters etc}

@@

Our findings showed that women’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.  The similar results also applied to women’s view of whether FGC should be continued \cf{link}.  \cfjd{How to use the future-mother producing daughter model?}.  Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .

— Norm —

- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. 
- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
- \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}

- community level of effects -

- tipping point/threshold -

— secondary analysis/socio demograhpic —

- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} .

— Suggestions —
- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.)

==================================
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}

@@

OVERALL:
% “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})
% Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}. It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).

— Second interpretation —
--- socio demographic interpretation at both levels (link this to modernization?)
\cite{Hayf05, PashPonn16} (more)
% education:  \cite{IliyAbub12, KarmKand11}
% religion:  \cite{KarmKand11}

— by nations —
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

@@

% FGC laws in those nations

=================
% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.

@@

@@

@@

@@

In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.  In Kenya, woman's decision on whether to cut their daughters' genitals were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.

@@

@@

====================================
\subsection{Funding}\label{Funding}
